\documentclass[12pt]{amsart}

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{times}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[psamsfonts]{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{latexsym}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{dsfont}

\makeatletter
\newtheorem*{rep@theorem}{\rep@title}
\newcommand{\newreptheorem}[2]{%
\newenvironment{rep#1}[1]{%
 \def\rep@title{#2 \ref{##1}}%
 \begin{rep@theorem}}%
 {\end{rep@theorem}}}
\makeatother

\hypersetup{
  colorlinks   = true,
  urlcolor     = blue,
  linkcolor    = blue,
  citecolor   = blue
}

\let\Pr\undefined
\def\Rset{\mathbb{R}}
\def\Nset{\mathbb{N}}
\def\vcdim{\text{VCdim}}
\def\pdim{\text{Pdim}}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\Pr}{\mathbb{P}}
\DeclareMathOperator*{\argmax}{\rm argmax}
\DeclareMathOperator*{\argmin}{\rm argmin}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\range}{range}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\Tr}{Tr}
\providecommand{\norm}[1]{\| #1 \|}
\providecommand{\frobp}[2]{\langle#1, #2\rangle_F}
\def\dqed{\relax\tag*{\qed}}

\newcommand{\set}[1]{\{#1\}}
\newcommand{\iprod}[2]{\left\langle #1, #2 \right\rangle}
\newcommand{\h}{\widehat}
\newcommand{\tl}{\widetilde}
\newcommand{\Alpha}{{\boldsymbol \alpha}}
\newcommand{\mat}[1]{{\mathbf #1}}
\newcommand{\be}{\mat{e}}
\newcommand{\bu}{\mat{u}}
\newcommand{\bh}{\mat{h}}
\newcommand{\n}{\mat{n}}
\newcommand{\K}{\mat{K}}
\newcommand{\N}{\mat{N}}
\newcommand{\0}{\mat{0}}
\newcommand{\w}{\mat{w}}
\newcommand{\x}{\mat{x}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\Ind}{\mathds{1}}
\newcommand{\1}{\mathds{1}}
\newcommand{\R}{\mathfrak{R}}
\newcommand{\e}{\epsilon}
\newcommand{\EQ}{\gets}
\newcommand{\wt}{\widetilde}
\newcommand{\ssigma}{{\boldsymbol \sigma}}
\newcommand{\tts}{\tt \small}
\newcommand{\TO}{\mbox{ {\bf to }}}

\newtheorem{theorem}{Theorem}
\newreptheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newreptheorem{lemma}{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newreptheorem{corollary}{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newreptheorem{proposition}{Proposition}

\newcommand{\ignore}[1]{}


\title[Election Outcomes]
{Accurate Prediction of Electoral Outcomes}

\begin{document}

\begin{abstract}
  We present a new on-line learning algorithm for predicting the
  outcome of large elections, using as input the predictions made by
  several experts. Our algorithm benefits from theoretical guarantees
  that we present and discuss in detail. We also report the results of
  experiments demonstrating the performance of our algorithm for
  predicting electoral results both in Australia and in the United
  States.

\end{abstract}

\maketitle

\section{Motivation}

Politicians and the general population largely rely on polls and
predictions made by various experts for the prediction of electoral
results.  The failure of recent predictions made by such experts in
the United Kingdom and the United States motivates the search for
better tools and techniques. This paper presents a series of
techniques based on on-line learning to tackle this problem.


\section{Preliminaries} 
\label{sec:preliminaries}

Let $I \subseteq \Rset$ be an open interval and $f\colon I \to \Rset$
a convex function. It is known that $f$ is Lipschitz continuous on any
interval $[a, b] \subset I$, $f$ admits both left and right
derivatives $f'_-$ and $f'_+$ over $I$, both non-decreasing, and 
$f$ is differentiable everywhere except for a set that is at most
countable.

\section{Taylor-type theorems}



\begin{lemma}
\label{lemma:absolute}
Let $I \subseteq \Rset$ be an open interval and $f\colon I \to \Rset$
a convex function. Then, the following holds for all $a, b \in I$:
\begin{equation*}
f(b) - f(a) = \int_a^b f'(t)\, dt = \int_a^b f'_+(t)\, dt = \int_a^b f'_-(t)\, dt.
\end{equation*}
\end{lemma}

\begin{proof}
  The result are based on \citep{MohriRostamizadehTalwalkar2012}.
  Since $f$ is Lipschitz continuous over the closed interval in $I$
  containing $a$ and $b$, it is absolutely continuous, which proves
  the first equality. The second equality is clear for Lebesgue
  integrals since $f'(t) = f'_+(t) = f'_-(t)$ for all but at most a
  countable set of points.
\end{proof}


\bibliographystyle{abbrv} 
\bibliography{fml2016-sample}
\end{document}
